\section{Project Information}
\begin{itemize}
  \item \textbf{Name:} Hashiwokakero.
  \item \textbf{Developing Environment:} Visual Studio Code (Windows, WSL).
  \item \textbf{Programming Language:} Python.
  \item \textbf{Libraries and Tools:}
        \begin{itemize}
          \item \textbf{Libraries:}
                \begin{itemize}
                  \item \href{https://docs.astral.sh/uv/getting-started/installation/}{\textbf{uv:}} An extremely fast Python package and project manager, written in Rust.
                  \item \href{https://pysathq.github.io/}{\textbf{PySAT:}} The power of SAT technology in Python
                        \begin{itemize}
                          \item \verb|pysat.formula.CNF|: class for manipulating CNF formulas.
                          \item \verb|pysat.solvers.Glucose42|: Glucose 4.2.1 SAT solver.
                          \item \verb|pysat.pb.PBEnc|: used for creating a CNF encoding of a weighted EqualsK constraint, i.e.\ of \(\sum_{i = 1}^{n}(a_i \cdot x_i) = k\)
                        \end{itemize}
                \end{itemize}
          \item \textbf{Tools:}
                \begin{itemize}
                  \item \href{https://git-scm.com/}{\textbf{Git}}, \href{https://github.com/}{\textbf{GitHub}}: Source code version control.
                  \item \href{https://chatgpt.com/}{\textbf{ChatGPT}}, \href{https://chat.deepseek.com/}{\textbf{DeepSeek}}: Scaffolding and debugging.
                  \item \href{https://code.visualstudio.com/}{\textbf{Visual Studio Code}}: Code editor for Python, Latex.
                \end{itemize}
        \end{itemize}
  \item \textbf{Demo video:} \href{https://drive.google.com/file/d/1kuBiLI41jVfF_J9hS3RkgJALv8Ot_QrW/view?usp=drive_link}{\textbf{Google Drive}}.
\end{itemize}
